The unequal distribution of access to education and transport: insights from

### 2016-06-06 paper.Rmd
New method figures, description for paper
Various updates to the paper

```{r, message=FALSE, eval=FALSE}
library(stplanr)
o = c(-46.31813, -23.38584) # coordinates of origin
d = c(-46.34078, -23.37746) # coordinates of origin
dist_google(from = o, to = d, mode = "transit")
```

@@

The code above takes an origin (`o`) and destination (`d`) and finds the travel time and distance. This is reported as 2962 metres and 2118 seconds (35 minutes) respectively. To ensure that the result was relevant to school travel, the times were calculated for arrival time at 9am on a weekday. The function was repeated for all origin-destination pairs.

@@

>>>>

```{r, message=FALSE, eval=FALSE}
library(stplanr)
o = c(-46.31813, -23.38584) # coordinates of origin
d = c(-46.34078, -23.37746) # coordinates of destination
dist_google(from = o, to = d, mode = "transit")
```

@@

The code above takes an origin (`o`) and destination (`d`) and finds the travel time and distance. This is reported as 2962 metres and 2118 seconds (35 minutes) respectively. To ensure that the result was relevant to school travel, the times were calculated for arrival time at 9am on a weekday. The function was repeated for all origin-destination pairs. To ensure the correct OD data was being generated, the results were plotted on an interactive map (Figure xx). The results show the high variability of route distance vs Euclidean distance ('circuity'), providing further evidence of inequalities in public transport provision in the city (Figure xx).

```{r , echo=FALSE, fig.cap="Visual representation of the 12,697 OD pairs routed through the Google Distance Matrix API on an interactive map in RStudio, an open source data analysis platform.", out.width="100%"}
knitr::include_graphics("od-map.png")
```

```{r euclid, echo=FALSE, fig.cap="Euclidean (straight line) vs public transport distances resulting from routing the 12,697 OD pairs of interest through the Google Distance Matrix API.", out.width="100%"}
knitr::include_graphics("public-vs-euclid-dists.png")
```

@@

\newpage
